Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe--Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v2.2)} \underline{Drafting Committee: DC90 (\today)}

### 2012-01-13 experiment_and_data.tex
Added covmat plot

\section{Experiment and Data Selection}
The new data presented in this work were collected in 2006 and 2007. As in ref.~\cite{Air09}, the data were collected with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples, respectively, are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$~\cite{Ben01}, with average beam polarisations of \red{$0.303$ and $0.392$.} \cite{tpol,lpol}. The procedure used to select events is similar to that used in ref.~\cite{Air09}.
A brief summary of this procedure is outlined in the following; consult
refs.~\cite{Zei09,Bur10} for more details.

>>>>

\section{Experiment and Data Selection}
The new data presented in this work were collected in 2006 and 2007. As in ref.~\cite{Air09}, the data were collected with the H{\sc ermes}
spectrometer \cite{Ack98} using the longitudinally polarised 27.6\,GeV
electron and positron beams incident upon an unpolarised hydrogen gas
target internal to the H{\sc era} lepton storage ring at D{\sc esy}. The integrated luminosities of the electron and positron data samples, respectively, are
approximately 246\,pb$^{-1}$ and 1460\,pb$^{-1}$, with average beam polarisations of \red{$0.303$ and $0.392$.} The procedure used to select events is similar to that used in ref.~\cite{Air09}. A brief summary of this procedure is outlined in the following; consult
refs.~\cite{Zei09,Bur10} for more details.

### 2012-01-13 results_dual.tex
Added covmat plot

The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data extractions. The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab\red{.}, and the collider experiments at H{\sc era}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In this model, the $t$ dependence is approximated by a physically motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the relevant amplitudes reported here are well described by the model.

>>>>

The curves in  figures~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the average value of the kinematic bins used for the data extractions. The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from H{\sc ermes} and Jefferson Lab\red{.}, and the collider experiments at H{\sc era}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In this model, the $t$ dependence is approximated by a physically motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06} at Hall A of Jefferson Laboratory; the model fit represented by the dashed curves includes these data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide results only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the relevant amplitudes reported here are well described by the model.
